\acknowledge{I was one of the few very lucky graduate students who had
the privilege to spend my graduate school years at the LIGO Livingston
Observatory. I got to learn how the interferometer works first-hand
and I had the privilege of getting to know and work with so many of
the world's top interferometer experts. Many thanks to my advisor,
Dave Reitze, for supporting my desire to reside at the site and for
spending a year there himself helping me get my thesis work underway
and well-defined for the next several years. Thank you, too, for all
of the phone calls over the years.

I wouldn't have made it all this way if it weren't for my teachers,
friends, and family who have served as role models throughout my life,
making me feel completely comfortable to pursue my interests,
including those in math and science. Special thanks to my Uncle Tom,
Jamie Lombardi, Ben Hummon, and Mrs.~Matts. Most of all, I thank my
parents, Janine and Alan, for their support and love all along the
way.

My LIGO career would not be if it weren't for the serendipitous timing
of chatting with my late neighbor, Noah Goldfish, who learned of my
SURF work and continued interest in LIGO. Noah introduced me to Andri
Gretarsson who in turn recommended me to the UF group. Thank you,
Andri. I am thankful for Guido Mueller, Dave Reitze, and David
Tanner's good judgement to recruit me only 2 months before the school
year started and despite the fact I had already accepted grad school
admission elsewhere. That was the best thing that could have happened
for me.

Thank you to all of my fellow graduate students who helped figure
things out with me and who made working at the sites all the more fun:
Tobin Fricke, Nicolas Smith, Dan Hoak, Anamaria Effler, Ryan DeRosa,
and Rupal Amin. Tobin deserves extra recognition for all that he
taught me and for his endless patience and encouragement.

Rana Adhikari always made sure I had one too many interesting projects
to work on and would bug me on my progress. It was nice to be looked
after. Thank you, Rana, and thanks for also teaching me to write good
elog entries. Thanks to Sam Waldman, Lisa Barsotti, and Matt Evans for
demonstrating how to be good scientists and for all the time you spent
at the sites. Thanks to Rai Weiss for his enthusiasm, for making me
make that first outline of my thesis, and for always being an advocate
for us students.

Thanks to the LLO staff and the UF LIGO group, especially Tom Evans
for letting me borrow his juggling clubs and Guido Mueller for being
so reasonable. And David Feldbaum says I must include a thank you for
him because I made him search the elog for a spiricon BCS picture one
too many times for me. Thank you, David!

Finally, this thesis would not be if it weren't for Valera Frolov, who
I thank sincerely for welcoming me as a fellow commissioner and for
being a role model on how to approach scientific work. He taught me to
think critically and could always be count on whether it be day,
night, or weekend, to offer advice and thought-provoking discussions.

This work was supported by the National Science Foundation through
grants PHY-0855313 and PHY-0555453. LIGO was constructed by the
California Institute of Technology and Massachusetts Institute of
Technology with funding from the National Science Foundation and
operates under cooperative agreement PHY-0757058.
}

